### 2024-06-08 Rebuttal/Response to Reviewer 1.tex

	\S~\red{2.2:}\\
	\VS{At $t = 0$, in our simulations, we release a spherical drop whose south pole is $0.05D_0$ away from the substrate and is falling with a velocity $V_0$. It is important to note that the drop may not be perfectly spherical and may have residual oscillations as they are released from the needle and arrive at the substrate. These oscillations are expected to be more pronounced for cases with small Weber and Ohnesorge numbers. The exact shape of the drop just before impact can influence the impact dynamics \citep{thoraval-2013-jfm, yun2017bouncing}. However, we suspect that the influence of these shape variations is captured, at least in part, by the error bars in the experimental data, which are derived from repeated trials under the same nominal conditions.}

	By acknowledging the possibility of residual oscillations and their potential influence on the impact dynamics, we aim to provide a more complete and transparent description of the experimental setup. We also highlight that the error bars in the experimental data, which are derived from repeated trials, likely account for some of the variability introduced by these shape variations.

	The inclusion of this discussion helps readers to better understand the limitations and uncertainties inherent in the experimental setup, and it provides important context for interpreting the results. We have also added references to relevant literature \citep{thoraval-2013-jfm, yun2017bouncing} that further explore the influence of drop shape on impact dynamics.

	\item \textit{How are the density, viscosity, and surface tension of the various water-glycerol mixtures determined? These also need to be reported.}

	We use the protocol described in \citet{cheng2008formula, volk2018density}. We have added a new table~\ref{tab:table00} with all the material properties (density, viscosity, and surface tension) of the water-glycerol mixtures used in this work.

	\begin{table}
		\begin{center}
			\def~{\hphantom{0}}
			\begin{tabular}{lccc}
				glycerol & $\rho_d$ & $\eta_d$  & $\gamma$\\
				(wt \%) &(kg/m$^{3}$) &(mPa.s)& (mN/m)\\[3pt]
				0 & 1000 & 1 & 72 \\
				50 & 1124 & 5 & 61 \\
				63 & 1158 & 10 & 61 \\
				74 & 1188 & 25.3 & 61 \\
				80 & 1200 & 45.4 & 61 \\
				85 & 1220 & 80.2 & 61 \\
			\end{tabular}
			\caption{\VS{Properties of the water-glycerol mixtures used in the experiments. $\rho_d$ and $\eta_d$ are the density and viscosity of the drop, respectively and $\gamma$ denotes the liquid-air surface tension coefficient. These properties are calculated using the protocol provided in \citet{cheng2008formula, volk2018density}.}}
			\label{tab:table00}
		\end{center}
	\end{table}

	\item \textit{Some details on the numerical implementation are left out. In particular, the computational domain size and initial conditions should be specified.}

	We have added these details in the revised manuscript:

	\S~\red{2.2:}\\
	\VS{The domain boundaries are far enough from the drop not to influence its impact process ($\mathcal{L}_\text{max} \gg D_0$, $\mathcal{L}_\text{max} = 8R$ in the worst case). At $t = 0$, in our simulations, we release a spherical drop whose south pole is $0.05D_0$ away from the substrate and is falling with a velocity $V_0$. It is important to note that the drops may not be perfectly spherical and may have residual oscillations as they are released from the needle and arrive at the substrate. These oscillations are expected to be more pronounced for cases with small Weber and Ohnesorge numbers. The exact shape of the drop just before impact can influence the impact dynamics \citep{thoraval-2013-jfm, yun2017bouncing}. However, we suspect that the influence of these shape variations is captured, at least in part, by the error bars in the experimental data, which are derived from repeated trials under the same nominal conditions.}

	\item \textit{The authors ignore the role of the air film in the dynamics on the grounds that the air-based Ohnesorge number is small, however the air gap can become extremely small and thus it is not clear that the drop diameter is the relevant length scale in assessing the viscous forces in the air. Furthermore, this is contrast to prior work on non-wetting impacts (such as Kolinski et al. (EPL 2014)) that argues viscous effects in the thin gas layer can play a role in the liquid dynamics. This should be discussed.}

	Thank you for raising this important point about the role of the air film in the drop impact dynamics. We appreciate the opportunity to discuss this aspect further and clarify its relevance to our work.

	We acknowledge that our treatment of the air film, based on the small air-based Ohnesorge number, may only partially capture the complexity of the viscous forces in the thin gas layer. The reviewer rightly points out that the drop diameter is not the most appropriate length scale for assessing these forces, especially when the air gap is extremely thin. This approach contrasts with some prior work on non-wetting impacts, such as \citet{kolinski-2014-epl}, which argues for the significance of viscous effects in the thin gas layer on the liquid dynamics. In fact, the air layer has two important contributions:

	\begin{enumerate}
		\item It prevents the contact between the falling drop and the solid surface. 
		\item It might lead to dissipation owing to the large velocity gradients. 
	\end{enumerate}

	To understand the relative importance of these two effects, we have recently conducted direct numerical simulations and compared the results with experiments on various surfaces, including superhydrophobic surfaces \citep{sanjay_chantelot_lohse_2023}, atomically smooth viscous films \citep{sanjay2023drop}, and even other drops \citep{ramirez2020lifting}. Our findings suggest that, for the macroscopic observables, the primary contribution of the air film is to prevent contact between the drop and the substrate. In contrast, the dissipation inside the air film itself does not play a significant role in the parameter range we study. This feature is particularly notable for large Weber numbers ($We$) where substrate-independent bouncing ceases.
	Despite the high-velocity gradients in the air film, we propose that the dissipation inside the drop dominates in all the cases we have examined. The small volume and low air viscosity limit the dissipation it can create, in contrast to the findings of previous works like \citet{kolinski-2014-epl}. However, we also acknowledge the complexity of modeling the air film, especially considering the extremely small Knudsen numbers involved. In such cases, a hybrid method \citep{chubynsky-2020-prl, sprittles2024gas} might provide a more accurate description.

	We have added a discussion of these points in the revised manuscript to provide a more comprehensive discussion of the role of the air film in drop impact dynamics and to address the apparent contrast with prior work. We thank the reviewer for highlighting this important aspect and helping us improve the clarity and completeness of our manuscript.

	\S~\red{2.2:}\\
	\VS{To ensure a perfectly non-wetting surface, we impose a thin air layer (minimum thickness $\sim \Delta/2$) between the drop and the substrate. This air layer prevents direct contact between the liquid and solid \citep{kolinski-2014-epl, sprittles2024gas}, effectively mimicking a perfectly non-wetting surface. The presence of this air layer is crucial for capturing the dynamics of drop impact on superhydrophobic surfaces, as it allows for the formation of an air cushion that can significantly affect the spreading and rebound behavior of the drop \citep{ramirez2020lifting, sanjay_chantelot_lohse_2023}.
	While this approach does not fully resolve the microscopic dynamics within the air layer itself, such as the high-velocity gradients and viscous dissipation inside the gas film once it thins below a critical size ($\sim 10\Delta$), it has been shown to accurately capture the macroscopic behavior of drop impact in the parameter range of interest \citep{ramirez2020lifting, sanjay2023drop, alventosa2023inertio, garcia2024skating}. We refer the readers to \citet{VatsalThesis} for discussions about this \lq\lq precursor\rq\rq, air film method and to \citet{popinet-basilisk, vatsal_sanjay_2023_7598181, zhang2022impact} for details on the numerical framework.}

	\item \textit{Figure 5 does not include any experimental data. This should be explained. Perhaps the high Oh regime is not accessible with the droplet sizes and fluids used?}

	Thank you for raising this important point about the experimental data in Figure 5. We appreciate your suggestion to consider using other liquids, such as silicone oil, to probe a wider range of viscosity and Ohnesorge number ($Oh$).
	In our experiments, we focused on using water-glycerol mixtures, which allowed us to explore two orders of magnitude in $Oh$. While silicone oil could indeed provide access to a broader viscosity range, it would require the use of superamphiphobic surfaces \citep{deng2012candle, ramirez2020lifting}. We have added a remark in the revised manuscript to acknowledge this limitation and to suggest potential future directions for exploring higher $Oh$ regimes using alternative liquid-surface combinations. This will help provide context for our experimental choices and highlight opportunities for further research.

	\S~\red{2.1:}\\
	\VS{Using other liquids like silicone oil could allow for a wider viscosity variation if used with a superamphiphobic substrate \citep{deng2012candle}.}

	\item \textit{Figure 5(a) partially confirms the $\sqrt{Oh}$ proposed, but suggests a notable $We$ dependence on the prefactor that is absent from the scaling argument. This should be analyzed and discussed.}

	Thank you for highlighting the $We$ dependence on the prefactor in Figure 5(a). We agree that this warrants further analysis and discussion in the manuscript.
	In the revised version, we have addressed this by examining the function $F_1(Re)$, where $Re = V_0D_0/\nu_d$ is the impact Reynolds number. This analysis focused on the low $Re$ regime, has allowed us to describe the $We$ dependence on the prefactor more effectively.
	We added a new Figure 5(c) to the manuscript to illustrate this relationship. However, it is important to note that some scatter is still observed at high $Re$ values, which can be attributed to the $We$ dependence of the impact force peak amplitude.
	By incorporating this additional analysis and discussion, along with the new Figure 5(c), we aim to provide a more comprehensive understanding of the factors influencing the scaling relationship.

	\S~\red{3.2:}\\
	\VS{Figure~5 further shows that these scaling laws are weakly dependent on the Weber number, as viscous dissipation consumes the entire initial kinetic energy of the impacting drop (figure~6). Once again, we stress that using the water-glycerol mixtures limits the range of $Oh$ that we can probe experimentally. 
	We further note that the first peak is robust and does not depend on the wettability of the substrate. Consequently, to compare with the existing data such as those in \citet{cheng2021drop} with different liquids to cover a wider range of liquid viscosities and to account for the apparent $We$-dependence, we plot $F_1$ compensated with $F_\rho$ against the impact Reynolds number $Re \equiv \frac{\sqrt{We}}{Oh} = V_0D_0/\nu_d$. 
	For the low $Re$ regime, such a plot allows us to describe the $We$ dependence on the prefactor more effectively, as illustrated in figure~5(c). However, it is important to note that some scatter is still observed at high $Re$ values, which can be attributed to the $We$ dependence of the impact force peak amplitude. This lack of a pure scaling behavior demonstrates how the interplay between kinetic energy and viscous dissipation within the drop dictates the functional dependence of the maximum impact force on $Oh$.}

	\item \textit{For the large $Oh$ impacts (section 3.2) the authors use the Rayleigh oscillation time as the timescale for impact. This theoretical timescale is derived for $Oh \ll 1$ droplet oscillations, and so is not clearly justified here. If $t_{\text{max}}$ is indeed independent of $Oh$ for the cases considered here, the authors should demonstrate this with their data. Furthermore, a physical interpretation of the overall trends predicted by the scaling arguments (3.16) and (3.17) should be provided.}

	Thank you for raising this important point about the use of the Rayleigh oscillation time as the timescale for impact in the large Ohnesorge number ($Oh$) regime. We appreciate the opportunity to clarify our approach and present the modifications made to the theoretical model based on your critique and our recent work \citep{sanjay2024PRL}.

	In the revised version of the manuscript, we have made two major changes to the model:

	\begin{enumerate}
		\item[$\bullet$] We now integrate until $\tau_\rho$ instead of $t_{\text{max}}$, as you correctly pointed out. The first peak appears within a fraction of $t \sim \tau_\rho$ (see Figures 3 and 4).
		\item[$\bullet$] For the viscous regime, we propose that the entire initial kinetic energy is lost from $t = 0$ until $t = \tau_\rho = D_0/V_0$. The viscous dissipation during this time frame dictates the drop impact force.
	\end{enumerate}

	With these modifications, the leading order of the model now gives $F_1 \sim 1/\sqrt{Re}$ (see Figure 5c of the revised manuscript or Figure~\ref{fig:F1Anatomy_2} of this reply). This result is consistent with the findings of \citet{Gordillo2018}. In fact, there is only a minor discrepancy between the theoretical results of \citet{Gordillo2018, cheng2021drop} and our direct numerical simulation data.

	However, we still recommend the need for a predictive model to obtain the first force peak amplitude $F_1$ based on the control parameters $We$ and $Oh$. We address this question in our recent work \citep{sanjay2024PRL}, where we use global energy balances to unify the scaling of drop impact forces in different parts of the parameter space. We have also added a brief discussion of this in the revised manuscript.

	Regarding the physical interpretation of the overall trends predicted by the scaling arguments (3.16) and (3.17), we have expanded on this in the revised manuscript. The scaling arguments capture the dominant force balance during the impact process, considering the relative importance of inertial, capillary, and viscous forces. The trends predicted by these scaling arguments provide insights into the key physical mechanisms governing the drop impact dynamics in different regimes.

	\S~\red{5:}\\
	\VS{Although, the implicit theoretical model summarized in \citet{cheng2021drop} describes most of data in figure~5, we stress the importance of having a predictive model to determine $F_1$ for given $We$ and $Oh$ \citep{sanjay2024PRL}.}

	\S~\red{3.2:}\\
	\blue{To systematically elucidate these scaling behaviors in the limit of small $Re$, we need to find the typical scales for the rate of change of kinetic energy and that of the rate of viscous dissipation for the drop impact system. First, we can readily define an average rate of viscous dissipation per unit mass as}

	\blue{\begin{align}
		\bar{\varepsilon} \sim \frac{1}{\tau_\rho}\frac{1}{D_0^3}\int_0^{\tau_\rho}\int_\Omega\nu_d\left(\boldsymbol{\mathcal{D}:\mathcal{D}}\right)d\Omega dt,
	\end{align}}

	\noindent \blue{where $\nu_d$ is the kinematic viscosity of the drop and $d\Omega$ is the volume element where dissipation occurs. Notice that $\bar{\varepsilon}$ has the dimensions of $V_0^3/D_0$, i.e., length squared over time cubed or velocity squared over time, as it should be for dissipation rate of energy per unit mass. We can estimate $\Omega = D_{\text{foot}}^2l_\nu$ (figure~6), where $D_{\text{foot}}$ is the drop's foot diameter in contact with the substrate and $l_\nu$ is the viscous boundary layer thickness.} \VS{This boundary layer marks the region of strong velocity gradients ($\sim V_0/l_\nu$) analogous to the \citet{mirels1955laminar} shockwave-induced boundary layer. For details, we refer the authors to \citet{schlichting2016boundary, Schroll2010, Philippi2016}. Consequently, the viscous dissipation rate scales as}

	\blue{\begin{align}\label{eq:dissipationScale}
		\bar{\varepsilon} \sim \frac{1}{\tau_\rho D_0^3}\int_0^{\tau_\rho}\nu_d \left(\frac{V_0}{l_\nu}\right)^2 D_{\text{foot}}^2l_\nu dt.
	\end{align}}

	\noindent \blue{To calculate $D_{\text{foot}}$, we assume that the drop maintains a spherical cap shape throughout the impact (figure~6). To calculate the distance the drop would have traveled if there were no substrate, we use the relation $d \sim V_0t$. Simple geometric arguments allow us to determine the relation between the foot diameter and this distance, $D_{\text{foot}} \sim \sqrt{D_0d}$ \citep{lesser1981analytic, mandre2009precursors,  zheng2021air, bilotto2023fluid, bertin2023similarity}.} \VS{Interestingly, this scaling behavior is similar to the inertial limit \citep{wagner1932stoss, Bouwhuis2012, Philippi2016, gordillo2019theory} as discussed by \citet{langley2017impact, bilotto2023fluid}.} \blue{Furthermore, the viscous boundary layer $l_\nu$ can be approximated using $\sqrt{\nu_d t}$ \citep{mirels1955laminar, Eggers2010, Philippi2016}. Filling these in \eqref{eq:dissipationScale}, we get}

	\blue{\begin{align}	
		\bar{\varepsilon} \sim \frac{1}{\tau_\rho D_0^2}\int_0^{\tau_\rho}\sqrt{\nu_d} V_0^3 \sqrt{t} dt,
	\end{align}}

	\noindent \blue{which on integration gives}

	\VS{\begin{align}\label{eq:eps0Final}
		\bar{\varepsilon} \sim \sqrt{\nu_d \tau_\rho}V_0^3/D_0^2, 
	\end{align}}

	\noindent \VS{where $\tau_\rho$ is the inertial time scale. Here, we assume that for highly viscous drops, all energy is dissipated within a fraction of $\tau_\rho$. Filling in \eqref{eq:eps0Final} and normalizing $\bar{\varepsilon}$ with the inertial scales $V_0^3/D_0$,}

	\VS{\begin{align}\label{eq:DissipationScale}
		\frac{\bar{\varepsilon}}{V_0^3/D_0} \sim \sqrt{\frac{\nu_d\tau_\rho}{D_0^2}} = \frac{1}{\sqrt{Re}} = \left(\frac{Oh}{\sqrt{We}}\right)^{1/2}.
	\end{align}}

	\noindent \blue{Next, the kinetic energy of the falling drop is given by}

	\blue{\begin{align}\label{eq:KEdissipation}
		\dot{K}(t) \equiv \frac{dK(t)}{dt} \sim \rho_dD_0^3\bar{\varepsilon},\quad\text{where } K(t) = \frac{1}{2}m\left(V(t)\right)^2,
	\end{align}}

	\noindent \blue{and $V(t)$ is the drop's center of mass velocity. The left-hand side of \eqref{eq:KEdissipation} can be written as}

	\blue{\begin{align}\label{eq:KE-powerTime}
		\dot{K}(t) = mV(t)\frac{dV(t)}{dt} = F(t)V(t).
	\end{align}}

	\noindent \blue{In equation~\eqref{eq:KE-powerTime}, $F(t)$ and $V(t)$ scale with the first impact force peak amplitude $F_1$ and the impact velocity $V_0$, respectively, giving the typical scale of the rate of change of kinetic energy as}

	\blue{\begin{align}\label{eq:KE-power}
		\dot{K}^* \sim F_1V_0.
	\end{align}}

	\noindent \blue{We stress that \eqref{eq:KE-power} states that the rate of change of kinetic energy is equal to the power of the normal reaction force, an observation already made by \citet{wagner1932stoss} and \citet{Philippi2016} in the context of impact problems. Lastly, at large $Oh$, viscous dissipation enervates kinetic energy completely giving (figure~6c, also see:  \citet{Philippi2016} and \citet{ Wildeman2016}),}

	\blue{\begin{align}\label{eq:force-Dissipation}
		\dot{K}^* \sim F_1V_0 \sim \rho_dD_0^3\bar{\varepsilon}
	\end{align}}

### 2024-06-08 Rebuttal/Response to Reviewer 1.tex

	\noindent \blue{Additionally, we use the inertial scales to non-dimensionalize  \eqref{eq:force-Dissipation} and fill in \eqref{eq:DissipationScale}, giving}

	\VS{\begin{align}
		\frac{F}{F_\rho} \sim \frac{\bar{\varepsilon}}{V_0^3/D_0} \sim \frac{1}{\sqrt{Re}} = \left(\frac{Oh}{\sqrt{We}}\right)^{1/2}
	\end{align}}

	\noindent \blue{and using $F_1t_1 \sim \rho_dV_0D_0^3 = F_\rho\tau_\rho$,}

	\VS{\begin{align}
		\frac{t_1}{\tau_\rho} \sim \left(\frac{\sqrt{We}}{Oh}\right)^{1/2}.
	\end{align}}

	\VS{In summary, we use energy and momentum invariance to elucidate the parameter dependencies of the impact force as illustrated in figure~5. The scaling arguments capture the dominant force balance during the impact process, considering the relative importance of inertial, capillary, and viscous forces. As the dimensionless viscosity of impacting drops increases, the lack of surface deformation increases the normal reaction force (3.16). Further, the invariance of incoming drop momentum implies that this increase in normal reaction force occurs on a shorter timescale (3.17).}

	\item \textit{Access to the code is greatly appreciated. However, I would suggest a permanent identifier be assigned to the version applied in the present study. This can be accomplished with Zenodo (integrated with Github), for instance.}

	Thanks a lot for the idea of using Zenodo. Interestingly, the code is already there. We have added it as a citation in the revised manuscript \citep{vatsal_sanjay_2023_7598181}.

	\item \textit{In the introduction, the authors describe water as a ``low-viscosity" liquid. In comparison to what? As the authors note, viscous effects in the problem are best described by $Oh$ which includes other dimensional parameters in addition to viscosity. Similarly, in the end of section 4, the authors describe their previous work demonstrating a critical viscosity whereas it should be a critical $Oh$ (or indeed a critical viscosity when all other parameters fixed).}\\[0.5mm]

	We have changed the abstract to read:

	\VS{The maximum spreading diameter $F_1$ and the time $t_1$ to reach it depend on inertial timescales for low viscosity liquids, remaining nearly constant for viscosities up to 100 times that of water. For high viscosity liquids, we balance the rate of change in kinetic energy with viscous dissipation to obtain new scaling laws: $F_1/F_\rho \sim \sqrt{Oh}$ and $t_1/\tau_\rho \sim 1/\sqrt{Oh}$,
	%For liquids like water, the amplitude $F_1$ and the time $t_1$ to reach it are governed by inertial timescales, insensitive to viscosity variations up to 100-fold. 
	%For liquids with viscosity much larger than that of water, beyond this viscosity-independent regime, we balance the rate of change in kinetic energy and the rate of viscous dissipation to obtain the scaling laws: $F_1 \sim F_\rho\sqrt{Oh}$ and $t_1 \sim \tau_\rho/\sqrt{Oh}$
	where $F_\rho$ and $\tau_\rho$ are the inertial force and time scales, respectively, which are consistent with our data.}\\[0.5mm]

	We have also changed critical viscosity to critical $Oh$ as rightly pointed out by the reviewer.

	\S~\red{3.2:}\\
	\blue{Recently, \citet{Jha2020, sanjay_chantelot_lohse_2023} showed that there} \VS{exists a critical $Oh$, two orders of magnitude higher than that of a $2\si{\milli\meter}$ diameter water drop}, \blue{beyond which drops do not bounce either, irrespective of their impact velocity.}
\end{enumerate}

\textit{Overall, the manuscript provides valuable new data, interesting and important conclusions, and successfully extends their prior work in the area to consider a more complete parameter space. It will be of value to the droplets community and thus deserves to be published once the above concerns are addressed in detail.}\\[0.5mm]

We thank the reviewer for the valuable feedback and hope that the revised manuscript has addressed all the concerns.

\printbibliography[title=References]
\end{document}

### 2024-06-08 Rebuttal/Response to Reviewer 2.tex

\addbibresource{../Main/ViscousDropImpact_v2.bib}
\nonfrenchspacing
\setlength\parindent{0pt}
\usepackage{siunitx}
\usepackage{xcolor}
\usepackage{mathrsfs}
\usepackage[colorlinks,citecolor=purple]{hyperref}
\newcommand*\blue{\textcolor{blue}}
\newcommand*\red{\textcolor{red}}
\newcommand{\VS}[1]{{\textcolor{orange}{#1}}}

\renewcommand{\thefigure}{R\arabic{figure}}

\usepackage[obeyFinal,colorinlistoftodos, textwidth=60mm, shadow]{todonotes}
% todonotes specific macros begin!
\newcommand{\todoInsertref}[2]{\todo[color=green!40, #1]{#2}}
\newcommand{\todoExplaininDetails}[2]{\todo[color=orange!40, #1]{#2}}
\newcommand{\todoUrgent}[2]{\todo[color=red!40, #1]{#2}}
\newcommand{\todoSansUrgent}[2]{\todo[color=yellow!40, #1]{#2}}
\extramargin
%% todonotes specific macros end!

%opening
\title{Reply to Referee 2}
\author{Vatsal Sanjay, Bin Zhang, Cunjing Lv, and Detlef Lohse}
\date{}
\begin{document}

\maketitle

\textit{The manuscript ``Inertia \& viscosity dictate drop impact forces," by Sanjay and coauthors, reports experimental and numerical evidence of drop impact under a wide range of conditions, covering cases in which surface tension, viscosity, or inertia become dominant. Their main focus is understanding the laws that govern the primary and secondary peak of force signals, $F_1$ and $F_2$, and the times at which they occur, $t_1$ and $t_2$. The authors provide physical arguments that elucidate the data dependency on two dimensionless control parameters, the Weber ($We$) and the Ohnesorge ($Oh$) number, establishing general scaling laws. The physics of several limiting cases is also described in detail, fulfilling a broad picture of the studied quantities in the space of parameters.}

\textit{This work addresses a profound and relevant question regarding drop impact, which has implications for many applications. To improve our understanding of the involved physical quantities, the authors perform and report several new experiments and simulations, extending the range of parameters of gathered data. Accordingly, the manuscript presents a regime map for the force peaks, constituting its main contribution. Thus, The goal is well-aimed, and evidence and theory support the results well. However, I still have some concerns that I include in the attached report, which the authors should address to assert and clarify several claims in the manuscript.}

\textit{The manuscript is well-structured, easy to understand, and phrased in excellent English. Figures are not only helpful but also beautiful. The authors disclose every necessary detail to understand the experiments and numerical simulations and how they complement. Also, the literature on this problem cited in the manuscript is comprehensive.}

\textit{In summary, this manuscript that studies the drop-impact force peaks dependency on Weber and Ohnesorge numbers provides new and relevant data and contributes with a necessary regime map on each of the quantities examined and in a broader range of the dimensionless number under study. I will be eager to recommend its publication in the Journal of Fluid Mechanics after the authors solve the points I raised in the attached report.}\\[2mm]

@@

We thank the referee for carefully reading our manuscript and providing valuable feedback and suggestions. We have reviewed the referee's comments and made changes based on their suggestions. Below, we offer a point-to-point reply to each of the referee's comments and include the changes made in the manuscript. The referee's comments are in italics, and our replies are in plain black. Changes in the manuscript are highlighted in orange.

\begin{enumerate}
	\item \textit{Line1: The title is misleading. As far as I understand,both $F_1$ and $F_2$, and $\tau_1$ and $\tau_2$, depend under some regimes on surface tension $\gamma$, but the title excludes surface tension as a relevant parameter in drop impact forces. Authors could explain this better or choose a title that reflects all the quantities under study.}

@@

	We agree with the reviewer that the title was misleading. Of course, all three: inertia, capillarity, and viscosity, play a role. Indeed, we have studied the role of inertial and capillarity in \citet{zhang2022impact}. We have now changed the title of the paper to:

	\VS{The role of viscosity on drop impact forces}

	\item \textit{Figure 2: Although there are several pressure and velocity maps, etc., to characterize the different regimes throughout the article, there is only a single force signal (figure 2). Would the article benefit from including force signals for at least limiting cases of the dimensionless parameters? Force signal, the easier way to experimentally characterize the phenomenon, should provide a simple signature of the regime at which the drop impact occurs.}

	 We thank the reviewer for this remark. To extend the comparison at different Ohnesorge numbers $Oh$, we have added two additional $F(t)$ curves in figure 2 (see figure~\ref{fig:summary}). Furthermore, throughout the manuscript, we present experimental data wherever available (see figures 3 and 7).

	 \item 
	 \begin{enumerate}
	 	 \item \textit{Line111-114: Previous studies have considered much broader ranges of viscosities (c.f. Cheng 2022 and references therein) using other liquids and solutions. Readers could be addressed for completeness.}
	 	\item \textit{Figure 5: The authors of several other studies have found that $F1/F_\rho$ depends solely on the Reynolds number (Re), collapsing curves in an extensive range of high Re numbers. Have the authors tried to remove the dependency on $\gamma$ (through Oh)? Since $Re \equiv \frac{\sqrt{We}}{Oh}$, I wonder if using it could collapse curves, at least in the low Oh limit.}	 	
	 \end{enumerate}

	Using water-glycerol mixtures allows us to probe two orders of magnitude in $Oh$ in the experiments. In the hindsight of finishing this project, we agree with the reviewer that using other liquids (such as silicone oil) will allow one to probe a wider range of viscosity  (and hence $Oh$). Of course, such liquids cannot be used with the superhydrophobic surfaces that we use in our work but would require superamphiphobic surfaces, such as the ones used in \citet{deng2012candle, ramirez2020lifting}. We have added this remark in the revised manuscript.

	\S~\red{2.1:}\\
	\VS{We note that using other liquids like silicone oil could allow for a wider range of viscosity variation if used with a superamphiphobic substrate \citep{deng2012candle}.}

	Unfortunately, we do not have experiments for $Oh \gg 1$ (figure 5). Nonetheless, we can compare our results with those in \citet{Gordillo2018, cheng2021drop} illustrating $F_1(Re)$, where $Re = V_0D_0/\nu_d$ is the impact Reynolds number. We were, indeed, able to collapse the data for low $Re$ (high $Oh$) limit. there is still some scatter at high $Re$ (low $Oh$) owing to the $We$ dependence of the impact force peak amplitude. We have added this as figure 5(c).

@@

	\S~\red{2.1:}\\
	\VS{We note that using other liquids like silicone oil could allow for a wider range of viscosity variation if used with a superamphiphobic substrate \citep{deng2012candle}.}

	Unfortunately, we do not have experiments for $Oh \gg 1$ (figure 5). Nonetheless, we can compare our results with those in \citet{Gordillo2018, cheng2021drop} illustrating $F_1(Re)$, where $Re = V_0D_0/\nu_d$ is the impact Reynolds number. We were, indeed, able to collapse the data for low $Re$ (high $Oh$) limit. there is still some scatter at high $Re$ (low $Oh$) owing to the $We$ dependence of the impact force peak amplitude. We have added this as figure 5(c).

	\S~\red{3.2:}\\
	\VS{Figure~5 further shows that these scaling laws are weakly dependent on the Weber number, as viscous dissipation consumes the entire initial kinetic energy of the impacting drop (figure~6). Once again, we stress that using the water-glycerol mixtures limits the range of $Oh$ that we can probe experimentally. 
	We further note that the first peak is robust and does not depend on the wettability of the substrate. Consequently, to compare with the existing data such as those in \citet{cheng2021drop} with different liquids to cover a wider range of liquid viscosities and to account for the apparent $We$-dependence, we plot $F_1$ compensated with $F_\rho$ against the impact Reynolds number $Re \equiv \frac{\sqrt{We}}{Oh} = V_0D_0/\nu_d$. 
	For the low $Re$ regime, such a plot allows us to describe the $We$ dependence on the prefactor more effectively, as illustrated in figure~5(c). However, it is important to note that some scatter is still observed at high $Re$ values, which can be attributed to the $We$ dependence of the impact force peak amplitude. This lack of a pure scaling behavior demonstrates how the interplay between kinetic energy and viscous dissipation within the drop dictates the functional dependence of the maximum impact force on $Oh$.}

	\item
	\begin{enumerate}
		\item \textit{Eq. 3.4: Following previous comments, results in the literature (e.g., Cheng 2022) include corrections as a function of Re in the low Re limit. Have the authors tried adding them to their expression to include both viscous and capillary contributions?}
		\item \textit{Eq.~3.7: I am still not convinced of the validity of averaging over $t_{\text{max}}$ in Eq.~3.7. Many assumptions under consideration are valid only for the early impact and not through the spreading regime, which scales as $t_{\text{max}}$. In order to convince the readers, authors need to address this.}
	\end{enumerate}

	Thank you for raising this important point about the use of the $t_{\text{max}}$ as the timescale for impact in the large Ohnesorge number ($Oh$) regime. We appreciate the opportunity to clarify our approach and present the modifications made to the theoretical model based on your critique and our recent work \citep{sanjay2024PRL}.

@@

	\noindent \blue{and using $F_1t_1 \sim \rho_dV_0D_0^3 = F_\rho\tau_\rho$,}

	\VS{\begin{align}
			\frac{t_1}{\tau_\rho} \sim \left(\frac{\sqrt{We}}{Oh}\right)^{1/2}.
	\end{align}}

	\VS{In summary, we use energy and momentum invariance to elucidate the parameter dependencies of the impact force as illustrated in figure~5. The scaling arguments capture the dominant force balance during the impact process, considering the relative importance of inertial, capillary, and viscous forces. As the dimensionless viscosity of impacting drops increases, the lack of surface deformation increases the normal reaction force (3.16). Further, the invariance of incoming drop momentum implies that this increase in normal reaction force occurs on a shorter timescale (3.17).}

	\begin{figure}
		\centering
		\includegraphics[width=0.9\textwidth]{../main/Figures/RegimeMaps_v3.pdf}
		\caption{\blue{Regime map in terms of the drop Ohnesorge number $Oh$ and the impact Weber number $We$ to summarize the two peaks in the impact force by showing the different regimes described in this work based on (a) the first peak in the impact force peak amplitude $F_1$ and (b) the second peak in the impact force peak amplitude $F_2$. Both peaks are normalized by the inertial force scale $F_\rho = \rho_dV_0^2D_0^2$. These regime maps are constructed using $\sim 1500$ simulations in the range $0.001 \leq Oh \leq 100$ and $1 \leq We \leq 1000$.} \VS{The gray solid line in (a) and dashed line in (b) mark the inertial--viscous transition ($Re = 1$) and the bouncing--no-bouncing transition \citep[$Oh_c = 0.53$ for $Bo = 1$, see][]{sanjay_chantelot_lohse_2023}, respectively.}}
		\label{fig:RegimeMaps}
	\end{figure}

	\item \textit{As a suggestion, I find that adding a Reynolds-number (tilted) axis, which nicely follows the slope of the central transition area of the white region of inset (a), will help readers to place previous experimental results in this regime map. It may be redundant, but still very helpful.}\\[0.1mm]

	We thank the review for this suggestion. We have modified figure 10 to include $Re = 1$ transition line (see figure~\ref{fig:RegimeMaps}).

\end{enumerate}
